Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-23 paper.tex
revision 6.3

\subsection{User Interface}
Several modifications have been planned in the OpenStack Dashboard in order to deal with the new features.
First of all, the Instance Launch Panel should be provided with a new field, 
where the user could assign an existent GPU pool, create a new one or leave the instance without accelerators of this kind.
As soon as the option ``New GPU Pool'' is chosen, the proper fields for the pool configuration would appear (see Figure~\ref{fig:ui-launch}).
Furthermore, a new panel with the existent GPUs displays all the information related to GPUs (see Figure~\ref{fig:ui-rgpus}).

>>>>

\subsection{User Interface}
Several modifications have been planned in the OpenStack Dashboard in order to deal with the new features.
First of all, the Instance Launch Panel should be extended with a new field, where the user could assign an existing GPU pool, create a new one, or keep the instance without accelerators of this kind.
When the option ``New GPU Pool'' is chosen, the proper fields for the pool configuration would appear (see Figure~\ref{fig:ui-launch}).
Furthermore, a new panel with the existent GPUs displays all the information related to GPUs (see Figure~\ref{fig:ui-rgpus}).
